%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/sarthakdargan}{\Large Sarthak Dargan}} & Email: \href{mailto:sarthak221995@gmail.com}{sarthak221995@gmail.com} \\
  \href{https://www.linkedin.com/in/sarthakdargan}{{LinkedIn Profile}} & Mobile: +91 9810437497 \\
\end{tabular*}

%-----------PROFESSIONAL SUMMARY-----------------
\section{Professional Summary}
\resumeItem{Summary}{~8 years of experience in crafting data into intelligence.}
\resumeItem{Key Points}{
Python, CrewAI, LLMs, Agentic AI, Fine Tune LLMs (SFT, GRPO), Retrieval Augmented Generation (RAG), Hugging Face, LangChain, PyTorch, Milvus Vector DB, Docker, TensorFlow, Amazon Web Services (AWS), EC2, Model Deployment, Natural Language Processing (NLP), Large Language Models, Generative AI (Gen AI), Machine Learning Algorithms, Prompt Engineering, Causal Models, SQL.
}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Birla Institute of Technology and Science Pilani (WILP)}{Pilani, India}
{M.Tech in Data Science and Engineering}{2020 -- 2022}
\resumeSubheading
{Punjab University, Patiala}{Patiala, Punjab}
{B.Tech in Computer Science and Engineering}{2013 -- 2017}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Senior Machine Learning Engineer}{PayPal, Bengaluru, India}
  {Apr'25 – CURRENT}{}
\resumeItemListStart
  \resumeItem{Enterprise Knowledge Retrieval System}{
    Built RAG pipeline for Confluence/Slack through hybrid search (BM25/semantic search) with Milvus vector DB and MS-MARCO re-ranker. Incorporated GPT-4 LLM, source attribution, OCR, and bidirectional context processing.}
  \resumeItem{Agentic Dispute Resolution Workflow}{
    Developed async multi-modal POC using Crew AI framework for personalized dispute resolution calls. Leveraged Redis state tracking, slot-based dialogue management, and adaptive conversation flow via GPT-4.}
\resumeItemListEnd

\resumeSubheading
  {Research Analyst II (Data Scientist – II)}{Amazon, Bengaluru, India}
  {May'21 – Apr'25}{}
\resumeItemListStart
  \resumeItem{Summarization Using LLMs}{
    Built summarization model leveraging Anthropic Claude and Mistral-7B for clear narrative consolidation of multi-source data.}
  \resumeItem{Causal Impact Analysis on 3P Seller Performance}{
    Conducted Difference-in-Differences study to determine insights effect on sales, achieving 1.35\% ATE on Gross Merchandise Sales.}
  \resumeItem{Vendor Recommendation Model}{
    Created a hybrid recommendation model using Approximate Nearest Neighbour (ANN) and AWS Lambda. Recommended strategies for 80+ vendors.}
\resumeItem{Customer Reviews Taxonomy Classification}{
    Utilized BERT-based classification to analyze reviews across a taxonomy of 60+ topics, achieving an F1 score of 76\%.}
\resumeItemListEnd

\resumeSubheading
  {Associate Data Science Consultant}{KPMG, Gurugram, India}
  {Aug'20 – May'21}{}
\resumeItemListStart
  \resumeItem{Investment Fund Recommendation Platform}{
    Designed a hierarchical clustering model to suggest targeted financial products based on firm trends and buying history.}
\resumeItemListEnd

\resumeSubheading
  {Specialist Programmer (Data Scientist)}{Infosys, Bengaluru, India}
  {Aug'17 – Aug'20}{}
\resumeItemListStart
  \resumeItem{Content Mining Platform}{
    Implemented entity extraction and content mining module using Na\"ive Bayes, Bidirectional LSTM, Random Forest, and SVM for Pharma/FMCG clients.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{PayPal 2025 Hackathon Finalist}{
Top 6 out of 160 submissions – Used Qwen-32B fine-tuning (SFT, GRPO on AppWorld dataset) improving task completion rates by 2.5x.}
\resumeSubItem{GitHub README Generator [Demo]}{
Implemented Crew AI agent orchestration system with Google GenAI LLM on GCP, Flask API (async processing), and Docker for automated documentation generation.}
\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Publications}
\resumeSubHeadingListStart
\resumeItem{Patent, 2023}{
System to identify product aspects customers love/dislike.}
\resumeItem{AMLC Lifestyle AI Workshop, 2023}{
Data-Driven Fashion Design Using Diffusion Models.}
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
\item \textbf{Technical Skills:} Python, CrewAI, LLMs, Retrieval Augmented Generation (RAG), Hugging Face, LangChain, PyTorch, Milvus Vector DB, Docker, TensorFlow, NLP, Gen AI, Encoder-Decoder Models, Machine Learning Algorithms, SQL. 
\item \textbf{Tools:} Redis, AWS Lambda, AWS Step Functions.
\item \textbf{Frameworks:} Crew AI Framework.
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}